Embedded Domain-Specific Languages:\\ Composable Interpretations with Dependencies

### 2015-04-01 paper/Main.tex
Typo
MRM template for paper sketching

To state that the semantic domain type i represents is part of a larger collection of types, we use the following type class

@@

\section{Extensibility in Both Dimensions}
So far we've only talked about extensibility in one dimension:

>>>>

To state that the semantic domain that type i represents is part of a larger collection of types, we use the following type class

@@

\section{Extensibility in Both Dimensions}
So far we've only talked about extensibility in one dimension: \textit{// to be continuted...}
